### 2024-02-02 ms.qmd
Updates

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", refit = FALSE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", refit = FALSE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

pvalue <- format_dec(sapply(estimates, pmcmc), 3)

@@

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
mod_deli <- readRDS(here("output/models/deli.rds"))
resid_deli <- residuals(mod_deli)
## L. guichenoti
mod_guich <- readRDS(here("output/models/guich.rds"))
resid_guich <- residuals(mod_guich)
```

@@

>>>>

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", "complete",  refit = FALSE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", "complete", refit = FALSE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

pvalue <- format_dec(sapply(estimates, pmcmc), 4)

@@

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
mod_deli <- readRDS(here("output/models/delicomplete.rds"))
resid_deli <- residuals(mod_deli)
## L. guichenoti
mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
resid_guich <- residuals(mod_guich)
```

@@

#### Results employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task

```{r, cleandata2}
#| label: cleandata2
# Cleaning the data to select only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task.
data <- read.csv(here("data/Learning.csv"))
percentage_per_lizard <- data %>%
  filter(trial_associative > 25 & trial_associative <= 35) %>%
  group_by(lizard_id) %>%
  summarise(percentage = mean(FC_associative == 1))
# Filter lizards where the percentage is at least 80%
filtered_lizards <- percentage_per_lizard %>%
  filter(percentage >= 0.8)
# Subset the original dataset based on the filtered lizard IDs
clean_df_2 <- data %>%
  filter(lizard_id %in% filtered_lizards$lizard_id) %>%
  filter(sum(is.na(FC_reversal)) <= 15) %>%
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>%
    mutate(temp = factor(temp,
      levels = c("23", "28"),
      labels = c("23" = "Cold", "28" = "Hot"))) %>%
    mutate(cort = factor(cort,
      levels = c("B", "A"),
      labels = c("B" = "CORT", "A" = "Control"))) %>%
    mutate(trial_reversal=as.numeric(trial_reversal)) %>%
  data.frame()
```

```{r, sampleSize2}
#| label: sampleSize2
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list_2 <- list()
for(i in 1:length(specie)){
  for(k in 1:length(hormone)){
    for(l in 1:length(temperature)){
      n_list_2[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df_2, specie[i], hormone[k], temperature[l])
      }
    }
  }
```

```{r, models2}
#| label: models2
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = FALSE)
write.csv(deli_2, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = FALSE)
write.csv(guich_2, file= "./output/Checking/guich.csv")
```

```{r, resultsRev2}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
deli_CORTCold_2 <- deli_2$b_trial_reversal
deli_ControlCold_2 <- (deli_2$'b_trial_reversal:cortControl' + deli_2$b_trial_reversal)
deli_CORTHot_2 <- (deli_2$'b_trial_reversal:tempHot' + deli_2$b_trial_reversal)
deli_ControlHot_2 <- (deli_2$'b_trial_reversal:cortControl:tempHot' + deli_2$b_trial_reversal + deli_2$'b_trial_reversal:cortControl' + deli_2$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold_2 <- guich_2$b_trial_reversal
guich_ControlCold_2 <- (guich_2$'b_trial_reversal:cortControl' + guich_2$b_trial_reversal)
guich_CORTHot_2 <- (guich_2$'b_trial_reversal:tempHot' + guich_2$b_trial_reversal)
guich_ControlHot_2 <- (guich_2$'b_trial_reversal:cortControl:tempHot' + guich_2$b_trial_reversal + guich_2$'b_trial_reversal:cortControl' + guich_2$'b_trial_reversal:tempHot')
```

```{r, tbl-data_2}
estimates_2 <- list(
  deli_CORTCold_2, deli_ControlCold_2, deli_CORTHot_2, deli_ControlHot_2, 
  guich_CORTCold_2, guich_ControlCold_2, guich_CORTHot_2, guich_ControlHot_2
mean_2 <- format_dec(sapply(estimates_2, mean), 3)
interval_025_2 <- format_dec(sapply(estimates_2, function(x) quantile(x,0.025)), 3)
interval_975_2 <- format_dec(sapply(estimates_2, function(x) quantile(x,0.975)), 3)
intervals_2 <- paste(interval_025_2, interval_975_2, sep = " , ")
pvalue_2 <- format_dec(sapply(estimates_2, pmcmc), 4)
table_df_2 <- data.frame(
  Mean = rep(mean_2, each = 1),
  CI = rep(intervals_2, each = 1),
  PValue = rep(pvalue_2, each = 1)
n_df_2 <- as.data.frame(do.call(rbind, n_list_2)) %>%
new_table_df_2 <- merge(table_df_2, n_df_2) %>%
real_table_2 <- flextable(new_table_df_2) %>%
real_table_2
